---
title: "airnow_PM2.5_sites"
author: "Jonathan Callahan"
date: "1/7/2022"
output: html_document
---

```{r setup, include = FALSE, fig.width = 8}
knitr::opts_chunk$set(echo = TRUE)
```

# Background

The US Forest Service [AirFire](https://portal.airfire.org) Group processes
real-time air quality data from [AirNow](https://portal.airfire.org). This 
data is used in research projects and on-line tools such as the 
[Fire & Smoke Map](https://fire.airnow.gov).

The `airnow_PM2.5_sites.csv` "known locations" file is queried and updated
during data processing and contains the most complete version of the spatial 
metadata associated with AirNow monitoring sites.

# Spatial Metadata

Spatial metadata in this dataset include core location metadata defined in 
**MazamaLocationUtils::coreMetadataNames**, the `AQSID` site identifier used by the
EPA as well as fields prefixed with `airnow_` which are specific to this dataset:

```{r data-columns, results = "hold"}
library(MazamaLocationUtils)

locationTbl <- readr::read_csv(
  "airnow_PM2.5_sites.csv",
  progress = FALSE,
  show_col_types = FALSE
)

dplyr::glimpse(locationTbl)
```

# Current Map

The interactive map below provides a quick preview of the status of the current
dataset.

```{r leaflet-map}
MazamaLocationUtils::table_leaflet(
  locationTbl,
  maptype = "terrain",
  extraVars = c(
    "AQSID", 
    "airnow_agencyName", 
    "airnow_status"
  ),
  radius = 6,
  color = "black",
  weight = 2,
  fillColor = "blue",
  fillOpacity = 0.2  
)
```
