---
title: "airnow_PM2.5_sites"
author: "Jonathan Callahan"
output: html_document
---

```{r setup, include = FALSE, fig.width = 8}
knitr::opts_chunk$set(echo = TRUE)
```

_Updated on `r strftime(lubridate::now(), "%B %d, %Y")`_

----

# Background

The US Forest Service [AirFire](https://portal.airfire.org) Group processes
real-time air quality data from [AirNow](https://portal.airfire.org). This 
data is used in research projects and on-line tools such as the 
[Fire & Smoke Map](https://fire.airnow.gov).

The `airnow_PM2.5_sites.csv` "known locations" file is queried and updated
during data processing and contains the most complete version of the spatial 
metadata associated with AirNow monitoring sites.

_NOTE:  The AirNow "known locations" file is imperfect because it contains
duplicated locations. This is needed to support the `AQSID` "site identifier"
that is provided as part of the AirNow "site locations". It is the combination
of `locationID` and `AQSID` that is unique._

# Spatial Metadata

Spatial metadata in this dataset include core location metadata defined in 
**MazamaLocationUtils::coreMetadataNames**, the `AQSID` site identifier used by the
EPA as well as fields prefixed with `airnow_` which are specific to this dataset.

Additional fields are generated through reverse geocoding web requests to
the following web services:

* [USGS Elevation Point Query Service](https://nationalmap.gov/epqs/)
* [OpenCage Geocoding API](https://opencagedata.com)

```{r data-columns, results = "hold"}
library(MazamaLocationUtils)

locationTbl <- readr::read_csv(
  "airnow_PM2.5_sites.csv",
  progress = FALSE,
  show_col_types = FALSE
)

dplyr::glimpse(locationTbl)
```

# Current Map

The interactive map below provides a quick preview of the status of the current
version of the dataset.

```{r leaflet-map}
MazamaLocationUtils::table_leaflet(
  locationTbl,
  maptype = "terrain",
  extraVars = c(
    "AQSID", 
    "airnow_agencyName", 
    "elevation",
    "address"
  ),
  jitter = 0,
  radius = 6,
  color = "black",
  weight = 2,
  fillColor = "blue",
  fillOpacity = 0.2  
)
```
