---
title: "wrcc_PM2.5_sites"
author: "Jonathan Callahan"
output: html_document
---

```{r setup, include = FALSE, fig.width = 8}
knitr::opts_chunk$set(echo = TRUE)
```

_Updated on `r strftime(lubridate::now(), "%B %d, %Y")`_

----

# Background

The US Forest Service [AirFire](https://portal.airfire.org) Group processes
real-time air quality data from [WRCC](https://wrcc.dri.edu/cgi-bin/smoke.pl). This 
data is used in research projects and on-line tools such as the 
[Fire & Smoke Map](https://fire.airnow.gov).

The `wrcc_PM2.5_sites_1000.csv` "known locations" file is queried and updated
during data processing and contains the most complete version of the spatial 
metadata associated with WRCC monitoring sites.

# Spatial Metadata

Spatial metadata in this dataset include core location metadata defined in 
**MazamaLocationUtils::coreMetadataNames**, the `AQSID` site identifier used by the
EPA as well as fields prefixed with `airnow_` which are copied from the AirNow
known locations table when WRCC monitors are found in the AirNow data stream.

Additional fields are generated through reverse geocoding web requests to
the following web services:

* [USGS Elevation Point Query Service](https://nationalmap.gov/epqs/)
* [OpenCage Geocoding API](https://opencagedata.com)

```{r data-columns, results = "hold"}
library(MazamaLocationUtils)
setLocationDataDir(".")

locationTbl <- table_load("wrcc_PM2.5_sites_1000")

dplyr::glimpse(locationTbl)
```

# Current Map

The interactive map below provides a quick preview of the status of the current
version of the dataset.

```{r leaflet-map}
MazamaLocationUtils::table_leaflet(
  locationTbl,
  maptype = "terrain",
  extraVars = c(
    "elevation",
    "address"
  ),
  jitter = 0,
  radius = 6,
  color = "black",
  weight = 2,
  fillColor = "blue",
  fillOpacity = 0.2  
)
```
